Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-31 sections/abstract.tex
Rewrote the abstract

\begin{abstract}
Software code review is an established method regarded as a best practice in Software Engineering to achieve a sufficient quality in software project.
Its main intention is to early identify defects before integrating changes.
Nowadays, Modern Code Review (MCR)\cite{Bacchelli2013a}, less formal and lightweight code reviews have received much attention and put into software development regularly in both industrial and OSS projects.
The main benefit of MCR is that in-person meetings are not required, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}.
Reviewers can find defects and discuss by adding comments through a code review tool or a mailing list.
Developers will then fix their changes following those comments.

% the freeform style of modern code review
Even though Modern Code Review has less process overhead, it can be less effective if not done properly.
\TODO{explain about our methods}

% some comments are not technically contributing

>>>>

\begin{abstract}
Modern Code Review (MCR) where reviewers virtually discuss proposed changes by adding comments through a code review tool or a mailing list has  received much attention recently due to its perceived cost-effectiveness and popularity with industrial and OSS projects. Recent studies have indicated a positive relationship between the number of review comments and code quality. However little research exists investigating how such discussion impacts software quality. In fact there has been concern that the informality of MCR encourages a focus on trivial, tangential, or unrelated  issues. Indeed we have observed that such comments are quite frequent and may even constitute the majority.  We conjecture that an effective MCR actually depends on having a substantive quantity of comments that directly impact a proposed change (or are "useful"). To investigate this, a necessary step requires distinguishing review comments that are useful to a proposed change from those that are not. For a large OSS project such as our Qt case study, manual assessment of the over 72,000 comments is a daunting task.  We propose that semantic similarity is a practical, cost-efficient, and empirically assurable approach for assisting with such assessments. Our case-study results indicate that our approach can classify comments with significant precision and recall and reduce classification effort by about 77\%.
